paper_figs_rotations201911 : create paper figures from rotation runs

### 2019-12-02 inst/documents/paper_figs_rotations201911.Rmd
figs

@@

# proportion of scenarios not reaching resistance thresholds

@@

# PRCC to show the sensitivity of the difference between rotation and sequence to inputs
# this can only be used for the experiments where all insecticides are the same
# (because in the ones where insecticides differ there are multiple values for each input)

@@

    x <- df_res_16[,in_cols]
    y <- df_res_16['rot_minus_seq']

@@

    gg <- ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = axis_text_x) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme(panel.grid.major.y = element_line(color = "grey", size = 1)) +
             ylim(-1,1) +
             #ggtitle(paste(strat_name[strategy_num])) +
             xlab(NULL)

>>>>

# filter just the 4 A expts
df_res_A <- dplyr::filter(df_res_16, idAD=="A")

@@

# count proportion of scenarios not reaching resistance thresholds

@@

# PRCC to show the sensitivity of the difference between rotation and sequence to inputs
# this can only be used for the experiments where all insecticides are the same
# (because in the ones where insecticides differ there are multiple values for each input)
# start by running on just A expts

@@

    x <- df_res_A[,in_cols]
    y <- df_res_A['rot_minus_seq']

@@

    gg <- ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = axis_text_x) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme(panel.grid.major.y = element_line(color = "grey", size = 1)) +
             ylim(-1,1) +
             #ggtitle(paste(strat_name[strategy_num])) +
             ggtitle("Effect of inputs on benefit of rotations, all A expts.") +
             xlab(NULL)
